---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


## Overview

`"binomial"` is a minimal [R](http://www.r-project.org/) package 
that provides functions to calculate probabilites of a Binomial random variable.

* `bin_variable` creates a coin object (of class `"binvar"`)
* `bin_probability()` calculates a binomial probability.
* `bin_distribution()` creates a `bindis` object, a binomial distribution.
* `bin_cumulative()` creates a `bincum` object, a cumulative binomial distribution.
* `plot()` method for a `"bindis"` or `"bincum"`object to plot graphs of the distribution.
* `bin_choose()` calculates the number of combinations of determined number of successes and trials.
* `summary()` method for a `"binvar"` object.

## Motivation

This package has been developed to practice some of the concepts
behind the creation of an R package.


## Installation

Install the development version from GitHub via the package `"devtools"`:

```r
# development version from GitHub:
#install.packages("devtools") 
# install "binomial" (without vignettes)
devtools::install_github("nahyungkim1220/binomial")
# install "binomial" (with vignettes)
devtools::install_github("nahyungkim1220/binomial", build_vignettes = TRUE)
```


## Usage

```{r}
library(binomial)
library(ggplot2)
# binvar
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1
# summary
binsum1 <- summary(bin1)
binsum1
# bin_probability
bin_probability(success = 2, trials = 5, prob = 0.5)
# bindis
dis <- bin_distribution(trials = 5, prob = 0.5)
dis
# plot bindis
plot(dis)
#bin_choose
bin_choose(n = 5, k = 2)
```
