---
title: "Introduction to Package Binomial"
author: "Audrey Kim"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to Package Binomial}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
library(ggplot2)
```


## Binomial function

The package `"binomial"` implements functions for calculating probabilities of a Binomial random variable, and related calculations such as the probability distribution, the expected value, variance, etc.

## Creating a Binomial Variable object "`binvar`"

You can display the trials and probability of success of an object `"binvar"` with the function "`bin_variable()`". 
"`bin_variable()`" takes in two arguments:  `trials` (number of trials) and `prob` (probability of success).
```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1
```

## Summary of `binvar`
Once you have defined an object `binvar`, you can create a nice list that invokes all the elements of the object. The function 'summary()' function gives you the full description of the object 'binvar'.
```{r}
binsum1 <- summary(bin1)
binsum1
```

## Mean 
Use `bin_mean()` to find the mean. Specify the number of `trials` and `probability` of success in its arguments. 
```{r}
bin_mean(10, 0.3)
```

## Variance
Use `bin_variance()` to find the variance. Specify the number of `trials` and `probability` of success in its arguments. 
```{r}
bin_variance(10, 0.3)
```

## Mode
Use `bin_mode()` to find the mode. Specify the number of `trials` and `probability` of success in its arguments. 
```{r}
bin_mode(10, 0.3)
```

## Skewness
Use `bin_skewness()` to find the sknewness. Specify the number of `trials` and `probability` of success in its arguments. 
```{r}
bin_skewness(10, 0.3)
```

## Kurtosis
Use `bin_kurtosis()` to find the kurtosis. Specify the number of `trials` and `probability` of success in its arguments.
```{r}
bin_kurtosis(10, 0.3)
```

## Binomial Probability
Use the function "`bin_probability()`" to find the binomial probability. It takes in three arguments: number of `success`, number of `trials`, and the `probability` of success.
Then, plug them into bin_probability.
```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
```

## Binomial Distribution
Create an object `bindis` with the function "`bin_distribution()`". It takes in two arguments: number of `trials` and `probability` of success. `bindis` will return a dataframe with two rows:  sucesses in the first column,  and probability in the second column.
```{r}
dis <- bin_distribution(trials = 5, prob = 0.5)
```

## Plot the Binomal Distribution
With `bindis` created, you can use the function 'plot()'to create a graphic with the binomial distribution.
```{r}
plot(dis)
```

## Binomial Cumulative Distrubution
Create an object `bincum` with the function "`bin_distribution()`". It takes in two arguments: number of `trials` and `probability` of success. `bincum` will return a dataframe with three rows: sucesses in the first column, probability in the second column, and cumulative in the third column.
```{r}
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
```

## Plot the Binomial Cumulative Distrubution
With `bincum` created, you can use the function 'plot()'to graphs the cumulative distribution.
```{r}
plot(dis2)
```

## Binomial Choose
"`bin_choose`"" is a function that calculates the number of combinations in which `k` successes can occur in `n` trials. It takes in two arguments: k and n.
```{r}
bin_choose(n = 5, k = 2)
bin_choose(5, 0)
bin_choose(5, 1:3)
```
